Barneby Lives usage example

### 2023-05-18 scripts/project_template.Rmd
function to parse dms to dd and create dms finished, onto making sf obs

library(parzer)

#' this function parses coordinates from DMS to decimal degrees
#'
#'@param x an input data frame to apply operations too
#'@param lat a name of the column holding the latitude values
#'@param long a name of the colymn holding the longitude values
#'@param dms are coordinates in degrees minutes seconds? TRUE for yes, FALSE for decimal degrees
dms2dd <- function(x, lat, long, dms){

  if(missing(lat)){
    lat = colnames(dummy_pts)[grep('lat', colnames(dummy_pts))] }
  if(missing(long)){
    long = colnames(dummy_pts)[grep('long', colnames(dummy_pts))] }

  if(missing(dms)){
    dms = long == parzer::parse_lon(long)
  }

  if(dms == T){
    x$latitude_dd = parzer::parse_lat(lat)
    x$longitude_dd = parzer::pase_lon(long)
  } else{
    colnames(x)[which(names(x) == lat)] <- 'latitude_dd'
    colnames(x)[which(names(x) == long)] <- 'latitude_dd'
  }

#  x[,c('latitude_dd', 'longitude_dd')] <- 
#    sapply(x[c('latitude_dd', 'latitude_dd')], as.numeric)

 # if(x$longitude_dd > 0){longitude_dd * -1}; 
#  if(x$latitude_dd < 0){latitude_dd * -1}

  # now overwrite the original DMS values in our exact format

  return(x)

  latitude_dms = paste0(
    'N ', parzer::pz_degree(x$latitude_dd),
    '°', round(parzer::pz_minute(x$latitude_dd), 2),
    "'", round(parzer::pz_second(x$latitude_dd), 2)
  )

  longitude_dms = paste0(
    'W ', parzer::pz_degree(x$longitude_dd), 
    '°', round(parzer::pz_minute(x$longitude_dd), 2), 
    "'", round(parzer::pz_second(x$longitude_dd), 2)
  )

}

@@

# str detect the lat column
# str detect the long column
# ensure input lat is North
# ensure input long is West
# str detect the datum column, else assume WGS84

>>>>

@@

 x <- x |>
    dplyr::relocate(any_of(
      c('longitude_dms', 'latitude_dms', 'latitude_dd', 'longitude_dd')), 
    .before = last_col())
```
